### 2024-11-26 paper/al.tex
Remove ambiguity

SpecTec introduces AL, an algorithmic specification language, for specifying
the prose specification.
Since the prose notation of the official specification is informal, it is
essential to rigorously define AL to ensure an unambiguous and correct
specification, rather than merely imitating the original.
We begin by outlining the ambiguity of the prose specification in
\cref{sec:prose-informal}.
Next, we propose a formal model for Wasm control flow in AL in
\cref{sec:model}.
We then define the syntax and the semantics of AL in \cref{sec:definition}.
Finally, we produce an executable Wasm specification using AL interpreter that
ensures the correctness of the specification in \cref{sec:exec-spec}.

\section{Ambiguity in the prose specification}
\label{sec:prose-informal}

@@

% Execute
On the other hand, some control instructions \textit{execute} a Wasm
instruction.
\cref{fig:if} represents the prose specification for the \texttt{if}
instruction, which executes a block instruction with instructions in the then
branch or the else branch based on the value in the stack.
However, the block instruction itself does not appeared in the actual code,
making its execution unclear in this context.
The situation become even more complicated when the block contains control
instructions, such as function call.
While the intended meaning can still be inferred, this informality introduces
ambiguity, leaving room for multiple interpretations.

>>>>

SpecTec introduces AL, an algorithmic specification language, for specifying
the prose specification.
Since the prose notation of the official specification is informal, it is
essential to rigorously define AL to ensure an correct specification, rather
than merely imitating the original.
We begin by outlining the informality of the prose specification in
\cref{sec:prose-informal}.
Next, we propose a formal model for Wasm control flow in AL in
\cref{sec:model}.
We then define the syntax and the semantics of AL in \cref{sec:definition}.
Finally, we produce an executable Wasm specification using AL interpreter that
ensures the correctness of the specification in \cref{sec:exec-spec}.

\section{Informality in the prose specification}
\label{sec:prose-informal}

@@

% Execute
On the other hand, some control instructions \textit{execute} a Wasm
instruction.
\cref{fig:if} represents the prose specification for the \texttt{if}
instruction, which executes a block instruction with instructions in the then
branch or the else branch based on the value in the stack.
However, the block instruction itself does not appeared in the actual code,
making its execution unclear in this context.
The situation become even more complicated when the block contains control
instructions, such as function call.
While the intended meaning can still be inferred, this informality leaves room
for wrong interpretations.
